---
title: "homework-basic-r-proficiency"
author: "Rob Wells"
date: "2024-08-23"
output: html_document
---

# Homework - Basic R Proficiency

This class exercise is a companion to the following chapter in Computational Text Analysis: [Ch. 11 Loading and Analyzing Data](https://wellsdata.github.io/CompText_Jour/docs/r-load-analyze-visualize.html)

#1: load tidyverse, rio and janitor libraries

```{r}
install.packages("rio")
install.packages("tidyverse")
install.packages("janitor")

```

#2: Import Data using read.csv:

<https://github.com/wellsdata/CompText_Jour/raw/main/data/mob_analysis_data.csv>

```{r}
MobAnalysisData <- read.csv("/Users/ninimtchedlishvili/CompText_Jour-main/data/mob_analysis_data.csv")
```

#3: Provide dimensions: Gives number rows, then columns

```{r}
nrow(MobAnalysisData)
ncol(MobAnalysisData)
```

#4: Show names of your columns

```{r}

colnames(MobAnalysisData)

```

#5: Check data types

```{r}

str(MobAnalysisData)

```

#6: Display the first six rows

```{r}

head(MobAnalysisData)
```

#7: Create a table counting the number of entries by year and display the top 5 results

```{r}

Top5entries <- MobAnalysisData %>% 
  count(Year) %>% 
  arrange(desc(n))
  


```

#8: Create a table that counts the different entries in the "keyword" column

```{r}

Keywordentried <- MobAnalysisData %>% 
  select(keyword) %>% 
  count(keyword) %>% 
  filter() 

head(Keywordentried)


```

#9: Create a simple column ggplot chart that shows the total entries by year

```{r}

ggplot(data = Top5entries) +
  geom_col(mapping = aes(x=Year, y=n, fill=n), position = "dodge") +
    theme(legend.position = "none")+
  labs(title = "Total Entried By Year",
       subtitle = "Mob Analysis Data", 
       caption = "Graphic By Nini Mtchedlishvili", 
       x = "year",
       y = "Number of Entries")

```
